### 2021-03-11 paper.Rmd
fix captioning
update reference
update section
getting artifacts
fix catpion

- Stop/start/reverse

\begin{figure*}[!h]
   \centering
         \includegraphics[width=0.5\textwidth]{figures/liminal-stop-pause-refresh.png}
\caption{The clustering example in figure \ref{fig:tsne-tour} using the liminal interface. Here a grand tour is displayed on the right hand side, with buttons allowing users to play, pause and refresh the tour animation.}
\label{fig:manual-tour}
\end{figure*}

> pull something from ggobi book?
> figure 8 illustration

@@

\begin{figure*}[!h]
  \centering
           \includegraphics[width=0.24\textwidth]{figures/mouse_sage_2c_gam3-001.png}
         \includegraphics[width=0.24\textwidth]{figures/mouse_sage_2c_gam3-016.png}
         \includegraphics[width=0.24\textwidth]{figures/mouse_sage_2c_gam3-038.png}
         \includegraphics[width=0.24\textwidth]{figures/mouse_sage_2c_gam3-074.png}

\caption{Selected frames from using a grand tour of mouse retina single cell RNA-seq data with the radial transformation described in @Laa2020-uv. Here the sage display was used to identify and verify cluster sepearation between the three highlighted clusters estimated from a clustering algorithm.}
\label{fig:mouse-cluster}
\end{figure*}

>>>>

## Basic Interactions

- Stop/start/reverse (Stuart)

\begin{figure*}
   \centering
         \includegraphics[width=0.5\textwidth]{figures/liminal-stop-pause-refresh.png}
\caption{The clustering example in figure \ref{fig:tsne-tour} using the liminal interface. Here a grand tour is displayed on the right hand side, with buttons allowing users to play, pause and refresh the tour animation.}
\label{fig:tour-controls}
\end{figure*}

@@

\begin{figure*}
  \centering
           \includegraphics[width=0.24\textwidth]{figures/mouse_sage_2c_gam3-001.png}
         \includegraphics[width=0.24\textwidth]{figures/mouse_sage_2c_gam3-016.png}
         \includegraphics[width=0.24\textwidth]{figures/mouse_sage_2c_gam3-038.png}
         \includegraphics[width=0.24\textwidth]{figures/mouse_sage_2c_gam3-074.png}

\caption{Selected frames from using a grand tour of mouse retina single cell RNA-seq data with the radial transformation. The sage display was used to identify and verify cluster sepearation between the three highlighted clusters estimated from a clustering algorithm.}
\label{fig:mouse-cluster}
\end{figure*}
